Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-06-28 experiement.tex
finxing typos

\subsection{Scenarios}
In the following, cascades can be connected in tandem, where each set of cascade
in parallel is called a ``level``, as illustrated on Figure
\ref{fig:cascade_level}.
Seven different simulations have been simulated, to evaluate the effectiveness
of an enrichment cascade when used outside of its designed scope :
\begin{itemize}
\item one as the reference calculation, with a single cascade designed to
    directly produce \gls{HEU} from natural uranium,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, without recycling the tails of each cascade
    sending their tails to the waste,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
    the tails of one level in the feed of the previous level of
    cascades (see Figure \ref{fig:cascade_level}).
\end{itemize}

@@

As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
\ref{fig:case3}, the different cascade levels required up to $2n+1$ timesteps
before it starts to enrich uranium, where $n$ corresponds to the level number.
This corresponds to the number of timesteps required for the material to
propagate from the natural uranium source to the n-th level, regardless of the
duration of the timestep (hour, day, month,...). This is also true for the
number of timesteps required to reach the equilibrium assays value in the tails
reprocessing cases.  As timestep can be artificially small or large, one will
only be considering equilibrium values flow rates and assays in the following
analysis.

>>>>

\subsection{Scenarios}
In the following, cascades can be connected in tandem, where each set of cascade
in parallel is called a ``level``, as illustrated in Figure
\ref{fig:cascade_level}.
Seven different simulations have been simulated, to evaluate the effectiveness
of an enrichment cascade when used outside of its designed scope :
\begin{itemize}
\item one as the reference calculation, with a single cascade designed to
    directly produce \gls{HEU} from natural uranium,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, without recycling the tails of each cascade
    sending their tails to the waste,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
    the tails of one level in the feed of the previous level of
    cascades (see Figure \ref{fig:cascade_level}).
\end{itemize}

@@

As it can be observed in Figures \ref{fig:case1}, \ref{fig:case2} and
\ref{fig:case3}, the different cascade levels required up to $2n+1$ timesteps
before it starts to enrich uranium, where $n$ corresponds to the level number.
This corresponds to the number of timesteps required for the material to
propagate from the natural uranium source to the $n$-th level, regardless of the
duration of the timestep (hour, day, month, etc.). This is also true for the
number of timesteps required to reach the equilibrium assays value in the tails
reprocessing cases.  As timestep can be artificially small or large, one will
only be considering equilibrium values of flow rates and assays in the following
analysis.

### 2018-06-28 results.tex
finxing typos

As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
don't have the same effect on the cascade behavior. While the models A and C,
allow a quick enrichment gain, with the cascades chaining, respectively
4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
4/21/61/90.

@@

As shown in Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
production rate, from $2$ to almost $20$ kg/y when using model A and C, and from
$17$ to $38$ kg/y with the model B. For the reference calculation where all the
available cascades are used within a single large cascade design for direct
\gls{HEU} production, the \gls{HEU} production rate is slightly over $50$ kg/y.

As Model A and C, relies on maintaining the cut values at each stages of the
cascade and share the same number of levels, have the exact same cascade
repartition across the different levels and the same \gls{HEU} production rate.

>>>>

As illustrated in Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
don't have the same effect on the cascade behavior. While the models A and C,
allow a quick enrichment gain, with the cascades chaining, respectively
4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
4/21/61/90.

@@

As shown in Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
production rate, from $2$ to almost $20$ kg/y when using models A and C, and from
$17$ to $38$ kg/y with the model B. For the reference calculation where all the
available cascades are used within a single large cascade design for direct
\gls{HEU} production, the \gls{HEU} production rate is slightly over $50$ kg/y.

As models A and C, rely on maintaining the cut values at each stages of the
cascade and share the same number of levels, have the exact same cascade
repartition across the different levels and the same \gls{HEU} production rate.
